\documentclass[12pt]{article}

\usepackage{mathptmx}
\usepackage{setspace}
\usepackage{csquotes}

\doublespacing

\title{WI Union President Application Responses}
\author{Alec Lowry}

\begin{document}

\maketitle

\section{Why are you interested in an officer position?}

    Since last semester I have been considering either a Union officer position or Hoofer Council President. My interest in the officer position is rooted in two things; (1) I feel like I am capable of holding the position and bringing things of value to the table (more on this in subsequent questions) and (2) I faced some issues with programming as Hoofer Outing President that stemmed from the integration of Hoofers and the rest of the Union more then they have in the past.  I figure that if I were to be Hoofer Council President next year, I would find myself in a similar situation, but if I were to be Union President, I could help facilitate smoother cooperation as someone who thoroughly understands Hoofer's operational structure.

\section{What skills and/or experiences have you had that are related to the position(s) for which you are applying?}

    The obvious one is I am the Hoofer Outing Club's President currently. Back in high school, I was a team captain for both my soccer and nordic skiing team. This semester I am working as an intern for a software development company where I primarily do dev work, but I am interning under the team lead as that is the position I'd like post-graduation.  While not directly transferable, I have been learning a lot about how to manage a group's productivity and mindset.

\section{What you have learned about yourself from working on a team in the past?}

    Something I know about myself is that I'm often a bit uncomfortable being in the spotlight, but when working in teams, especially when I'm managing them, I've found that helps focus me on supporting the people around me. With the Outing Club, I've come to realize that one of my stand out traits is understanding the large picture and helping penetrate the abstraction and guide others through actionable sub-problems. In contrast, I have found that while I can be productive in an empirical sense, I struggle with motivating and building a solid ``team culture''. It is/has been an area of growth for me.


\section{What do you hope to accomplish as a Wisconsin Union student leader?}

    For myself, I'd like develop my management skills. Thus far, the majority of my leadership experience has been with people I've gotten to know before taking a position.  I anticipate that this opportunity will stretch my interpersonal skills. For the position, (1) I am hoping to help facilitate a smooth transition to in-person programming (who knows), (2) I love organizing and improving internal organization/systems, usually starting with onboarding/documentation, and (3) I'd like to bring my perspective as an involved Hoofer leader to aid in bring the greater Union and Hoofers closer together.

\section{What are all the activities, leadership positions or employment that you will have during the next academic year?}

    If 2021/2022 sees a return to in-person programming, I will likely be chasing a lot of hoofer involvement as a trip leader, but that is as my schedule allows. Otherwise, just school and this.

\end{document}
